\begin{itemize}

\item[\textbf{(info)}]
Since power and energy costs, both operational and capital, are increasingly significant, 
it is very important to understand the power and energy efficiency requirements of the system.  
This is best understood when running workloads, either applications or benchmarks.  
Each site will have to select the workloads to run as part of the procurement and 
acceptance process.  These workloads may differentially exercise or stress various 
subsystems: compute (CPU, GPGPU, etc.), I/O, Networks (Internal, facility and WAN).  
They may focus on applications that are based on integer as well as floating point computations.

\item[\textbf{(mandatory)}]
[Customer] shall specify the set of benchmarks [Customer] wants. Vendors shall 
provide the power and energy efficiency requirements as welll as the run times 
of a set of benchmarks. 

\item[\textbf{(mandatory)}]
The problem types in the benchmarks shall cover compute problems, memory problems, 
networking problems, and idle and sleep system states.

\item[\textbf{(info)}]
Suggested examples: HPL (compute problem), Integer-dominant codes (compute problem), 
Graph500 (memory/networking problem), GUPS, GUPPIE,  mySQL and non-mySQL database 
applications, and systemBurn developed at ORNL. 

\item[\textbf{(mandatory)}]
Customers shall specify the run rules and the measurement quality. Each benchmark 
must be measurable using the Green500 run rules and attain a Level 2 measurement quality. 

\item[\textbf{(important)}]
Customers shall specify the run rules and the measurement quality. Each benchmark 
must be measurable using the Green500 run rules and attain a Level 3 measurement quality. 

\item[\textbf{(important)}]
Vendors shall work with Customers to provide the power and energy effiency requirements 
of a set of site-supplied workloads. These workloads will reflect the typical case, 
not the extremes, so that vendors can design around the typical case. 

\item[\textbf{(important)}]
Customers may also require application power profiles with power and energy requirements.
\end{itemize}

