\begin{itemize}

\item[\textbf{(info)}]
The vendor shall provide [equipment, services and/or resources] that \textemdash among 
other objectives \textemdash establish a highly energy efficient solution at 
justifiable cost.  The proposed solutions should demonstrate net benefits under 
normal production conditions.  
\end{itemize}

\section{Energy-related Total Cost of Ownership (TCO)}

\begin{itemize}

\item[\textbf{(enhancing)}]
It is an objective of [Customer] to encourage innovative programs whereby the 
vendor and/or [Customer] are incentivized to reduce the costs for energy and/or 
power-related capital expenditures as well as the operational costs for energy.  
This may be for the system, datacenter and/or broader site.  By doing this, the 
vendor would be reducing the energy-related TCO for [Customer].  The vendor is 
encouraged to describe vendor support for these innovative programs in qualitative 
as well as quantitative terms.

\item[\textbf{(info)}]
An example of an innovative program for bringing the energy/power element of 
TCO to the front was used by LRZ.  LRZ's  procurement was based on TCO whereby the 
budget covered not just investment and maintenance, but operational costs as well. 
The intent was to provide a clear incentive for the vendor to deliver a solution that 
would yield low operational costs and, thereby, lower TCO.

\end{itemize}

\section{Power Usage Effectiveness (PUE)}

\begin{itemize}

\item[\textbf{(info)}]
It is an objective of [Customer] to run a highly energy efficient datacenter.  
One measure for datacenter efficiency is PUE.  It is recognized that the metric PUE 
has limitations.  For example, solutions with cooling subsystems that are built 
into the computing systems will result in a more favorable PUE than those that rely 
on external cooling, but are not necessarily more energy efficient.  In spite of 
these limitations, PUE is a widely adopted metric that has helped to drive energy efficiency.

\item[\textbf{(enhancing)}]
The US Department of Energy Office of the Chief Information Officer has set a 
requirement to achieve an average PUE of 1.4 by 2015.  As a result, the vendor 
is encouraged to qualitatively describe their support for helping [Customer] to 
meet this requirement.

\end{itemize}

\section{Total Usage Effectiveness (TUE)}

\begin{itemize}

\item[\textbf{(info)}]
TUE is another metric that has been developed to overcome the limitations of the 
PUE metric.  Specifically, it resolves the issue of PUE differences due to infrastructure 
loads moving from inside to outside the box.  TUE is the total energy into the datacenter 
divided by the total energy to the computational components inside the IT equipment.

\item[\textbf{(enhancing)}]
The vendor is encouraged to qualitatively describe their support for measuring TUE.
\end{itemize}

\section{Energy Re-Use Effectiveness (ERE)}

\begin{itemize}

\item[\textbf{(info)}]
Some sites have the ability to utilize the heat generated by the datacenter for productive 
uses, such as heating office space.  Energy re-use is not strictly adding to the energy 
efficiency of either the computing system or the datacenter, but it can reduce the energy 
requirements for the surrounding environment.  For those sites, it would be an objective 
of [Customer] to achieve an ERE \textless 1.0.  

\item[\textbf{(enhancing)}]
The vendor is encouraged to qualitatively describe their support for helping [Customer] 
to achieve an ERE \textless 1.0.  

\end{itemize}

\section{Power Distribution}
\begin{itemize}
\item[\textbf{(important)}]
The vendor is encouraged to qualitatively describe energy efficient and innovative 
solutions that help to reduce conversion losses in the datacenter.
\end{itemize}

